# Simple Linear Regression

<br>

The fundamental phenomenon suggested by the study is that better looking teachers are evaluated more favourably. 
The variable `bty_avg` is the average beauty rating of lecturer (where 1 is the lowest and 10 is the highest). Let's create a scatterplot of these variables to see if there appears to be a relationship:

```{r scatter, eval = FALSE}
ggplot(data = evals, aes(x = bty_avg, y = score)) +
  geom_point(color = "salmon2")
```

Before we draw any conclusions from the plot we can re plot using `geom_jitter`.

```{r scatter-jitter, eval = FALSE}
ggplot(data = evals, aes(x = bty_avg, y = score)) +
  geom_jitter(color = "skyblue2")
```

`geom_jitter` adds a small amount of random variation to the location of each point, it is a useful way of handling overplotting caused by discreteness in the data. 


From the scatterplot there appears to be a (slight) positive relationship between evaluation score and average beauty. However, we can see if the apparent trend in the plot is something more than natural variation by fitting a linear model to predict average lecturer score by average beauty rating.
    
Add the line of the best fit model to your plot using the following:
    
```{r scatter-score-bty_avg-line-se, eval = FALSE}
ggplot(data = evals, aes(x = bty_avg, y = score)) +
  geom_jitter() +
  geom_smooth(method = "lm")
```

`geom_smooth` aids in seeing patterns in the presence of overplotting. In the code above, it fits a linear model using `method = "lm"` and fits the line of best fit over the plot of `bty_avg` and `score`. The blue line is the model fitted. The shaded grey area around the line is called a "confidence band" and tells you about the variability you might expect in your predictions. To remove the confidence band, use `se = FALSE`.

<br>

**Does it appear that average beauty score is a predictor of lecture evaluation score?**

```{r, echo = FALSE}
q_avgb <- sample(c(
   "No",
   answer = "Yes"
)
)
```

`r longmcq(q_avgb)`

<br>

## **Exercise 3**

Produce residual plots to evaluate whether the conditions of least squares regression are reasonable. 

**Hint** Create a model object first, e.g. using `model1 <- lm(score ~ bty_avg, data = evals)`, then produce the plots.

`r hide("Hint 1")`

```{r hint3, eval = FALSE, echo = TRUE}
model1 <- lm(???)

ggplot(data = ???, aes(???)) +
  geom_point(color = "seagreen2") +
  geom_hline(???) +
  xlab(???) +
  ylab(???)

ggplot(data = ???, aes(???)) +
  geom_histogram(bins = 40, fill = "dodgerblue2") +
  xlab(???)

ggplot(data = ???, aes(???)) +
  stat_qq() +
  stat_qq_line(col = 2)
```

`r unhide()`

`r hide("Hint 2")`

```{r hint3_2, eval = FALSE, echo = TRUE}
model1 <- lm(score ~ bty_avg, data = evals)

ggplot(data = ???, aes(???)) +
  geom_point(color = "seagreen2") +
  geom_hline(???) +
  xlab("Fitted values") +
  ylab("Residuals")

ggplot(data = ???, aes(???)) +
  geom_histogram(bins = 40, fill = "dodgerblue2") +
  xlab("Residuals")

ggplot(data = ???, aes(???)) +
  stat_qq() +
  stat_qq_line(col = 2)
```

`r unhide()`


`r hide("Solution")`

```{r sol3, eval = FALSE, echo = TRUE}
model1 <- lm(score ~ bty_avg, data = evals)

ggplot(data = model1, aes(x = .fitted, y = .resid)) +
  geom_point(color = "seagreen2") +
  geom_hline(yintercept = 0, linetype = "dashed") +
  xlab("Fitted values") +
  ylab("Residuals")

ggplot(data = model1, aes(x = .resid)) +
  geom_histogram(bins = 40, fill = "dodgerblue2") +
  xlab("Residuals")

ggplot(data = model1, aes(sample = .resid)) +
  stat_qq() +
  stat_qq_line(col = 2)
```

`r unhide()`

<br>

**From the residuals, does it appear that the conditions of least squares regression are reasonable?**

```{r, echo = FALSE}
q_resid <- sample(c(
   "No, since the residuals aren't scattered evenly above and below the zero line, the histogram does not look bell shaped and centred at zero since and many of the QQ-plot points are very far from the line",
   answer = "Yes, since the residuals are scattered evenly above and below the zero line and while neither the histogram nor the QQ-plot are perfect, they both look adequate to show the residuals are approximately normally distributed."
)
)
```

`r longmcq(q_resid)`

<br>
