# Multiple Predictors

<br>

In order to see if beauty is still a significant predictor of lecturer score after you've accounted for the lecturer's gender, you can add the gender term into the model.

```{r model2, eval = FALSE}
model1 <- lm(score ~ bty_avg, data = evals)
summary(model1)

model2 <- lm(score ~ bty_avg + gender, data = evals)
summary(model2)
```

<br>

## **Exercise 4**

Produce residual plots for `model2` created above.

`r hide("Hint 1")`

```{r hint4, eval = FALSE, echo = TRUE}
model2 <- lm(???)

ggplot(data = ???, aes(???)) +
  geom_point(color = "seagreen2") +
  geom_hline(yintercept = 0, linetype = "dashed") +
  xlab(???) +
  ylab(???)

ggplot(data = ???, aes(???)) +
  geom_histogram(bins = 40, fill = "dodgerblue2") +
  xlab(???)

ggplot(data = ???, aes(???)) +
  stat_qq() +
  stat_qq_line(col = 2)
```

`r unhide()`

`r hide("Hint 2")`

```{r hint4_2, eval = FALSE, echo = TRUE}
model2 <- lm(score ~ bty_avg + gender, data = evals)

ggplot(data = ???, aes(???)) +
  geom_point(color = "seagreen2") +
  geom_hline(yintercept = 0, linetype = "dashed") +
  xlab("Fitted values") +
  ylab("Residuals")

ggplot(data = ???, aes(???)) +
  geom_histogram(bins = 40, fill = "dodgerblue2") +
  xlab("Residuals")

ggplot(data = ???, aes(???)) +
  stat_qq() +
  stat_qq_line(col = 2)
```

`r unhide()`


`r hide("Solution")`

```{r sol4, eval = FALSE, echo = TRUE}
model2 <- lm(score ~ bty_avg + gender, data = evals)

ggplot(data = model2, aes(x = .fitted, y = .resid)) +
  geom_point(color = "seagreen2") +
  geom_hline(yintercept = 0, linetype = "dashed") +
  xlab("Fitted values") +
  ylab("Residuals")

ggplot(data = model2, aes(x = .resid)) +
  geom_histogram(bins = 40, fill = "dodgerblue2") +
  xlab("Residuals")

ggplot(data = model2, aes(sample = .resid)) +
  stat_qq() +
  stat_qq_line(col = 2)
```

`r unhide()`

<br>

**From the residuals, does it appear that the conditions of least squares regression are reasonable?**

```{r, echo = FALSE}
q_resid2 <- sample(c(
   "No",
   answer = "Yes"
)
)
```

`r longmcq(q_resid2)`

<br>

**Is `bty_avg` still a significant predictor of `score`?**

```{r, echo = FALSE}
q_btyavg <- sample(c(
   "No",
   answer = "Yes"
)
)
```

`r longmcq(q_btyavg)`

<br>

**Has the addition of `gender` to the model changed the parameter estimate for `bty_avg`?**

```{r, echo = FALSE}
q_genadd <- sample(c(
   "No",
   answer = "Yes"
)
)
```

`r longmcq(q_genadd)`

<br>

**Has the addition of `gender` to the model provided a better model fit?**

```{r, echo = FALSE}
q_addfit <- sample(c(
   "No",
   answer = "Yes"
)
)
```

`r longmcq(q_addfit)`

<br>

*Note* the estimate for `gender` is now called `gendermale` in `model2` above. We can see this name change whenever we introduce a categorical variable. The reason is that R re-codes `gender` from having the values of `male` and `female` to being an indicator variable called `gendermale` that takes a value of $0$ for female lecturers and a value of $1$ for male lecturers. (Such variables are often referred to as "dummy" variables).  The fitted model (`model2`) is therefore:

\[
\begin{aligned}
\widehat{score} &= \hat{\beta}_0 + \hat{\beta}_1 \times bty\_avg + \hat{\beta}_2 \times gendermale \\
&= 3.75 + 0.07 \times bty\_avg + 0.17 \times gendermale 
\end{aligned}
\]

<br>

## Interpretation of a Categorical Variable with 2 levels

<br>

The interpretation of parameters associated with categorical variables is slightly different than numerical variables. This is described within, <a href="https://www.openintro.org/redirect.php?go=os4_tablet&referrer=/stat/os4.php#page=323" target="_blank">OpenIntro Section 8.2.8 Page 323</a>. 

The first two terms $\hat{\beta}_0 + \hat{\beta}_1 \times bty\_avg$ give the expected score for the first or *baseline* category or *reference level* (i.e. the category corresponding to an indicator value of 0), in this example female lecturers. The third term $\hat{\beta}_2 \times gendermale$  only appears for male lectures (i.e. when `gendermale = 1`) since the baseline is female, so for female lecturers, $\hat{\beta}_2$ is multiplied by zero. $\hat{\beta}_2$ is therefore the average change in the response variable between the two categories.  So the estimated parameter value of 0.17239 from `model2` above is the difference in the average evaluation score between male and female lecturers, with the average male's score being 0.17239 **more** than the average female score (when all other variables are held constant).   The fitted model showing the relationships between `score` and `bty_avg` for the levels of `gender` can be shown by using the fitted values stored in `model2` as follows:

```{r genderlines, eval = TRUE} 
library(broom)
model2 <- lm(score ~ bty_avg + gender, data = evals)
model2_aug <- augment(model2)

ggplot(data = model2_aug, mapping = aes(y = score, x = bty_avg, color = gender)) +
  geom_point(alpha = 0.3) +
  geom_line(aes(y = .fitted), lwd = 1)

``` 

<!-- # ggplot(data = evals, aes(x = bty_avg, y = score, color = gender)) +  -->
<!-- #           geom_smooth(method = "lm", formula = y ~ x, se = FALSE)  -->

The `augment` function is part of the `broom` package and makes information from the fitted model more accessible.  This plot shows why this model is referred to as a 'parallel lines model'.


The decision to call the indicator variable `gendermale` instead of `genderfemale` has no deeper meaning. RStudio simply codes the category that comes first alphabetically as a $0$.  You can change the reference level of a categorical variable, which is the level that is coded as a 0, using the`relevel()` function. Use `?relevel` to learn more.

<br>

### **Exercise 5**

Create a new model called `model3` with `gender` removed and `rank` added in. Then produce the model summary.

`r hide("Hint")`

```{r hint5, eval = FALSE, echo = TRUE}
model3 <- lm(???)

summary(???)
```

`r unhide()`


`r hide("Solution")`

```{r sol5, eval = FALSE, echo = TRUE}
model3 <- lm(score ~ bty_avg + rank, data = evals)

summary(model3)
```

`r unhide()`

<br>

*Note* that the rank variable has three levels: `teaching`, `tenure track`, `tenured` (look back at the boxplots in Exercise 2 in the "Exploratory Data Analysis" section).

<br>

## Interpretation of a Categorical Variable with more than 2 levels

<br>

The interpretation of the coefficients associated with categorical variables in multiple regression is covered in <a href="https://www.openintro.org/redirect.php?go=os4_tablet&referrer=/stat/os4.php#page=344" target="_blank">OpenIntro Section 9.1.1 Page 344</a>. 

When fitting a regression model with a categorical variable that has k levels where $k > 2$, **R** provides a coefficient for $k − 1$ of those levels.  Therefore, one 
level does not receive a coefficient and this is the *reference level* or *baseline*.  The coefficients listed for the other levels are all estimates of the difference between the respective levels to the reference level, *while holding all other variables constant*.

The estimate for `bty_avg` estimates the change in expected evaluation score for every unit increase in beauty rating *while holding all other variables constant*. In this case, that translates into considering only lecturers of the same rank with `bty_avg` scores that are one point apart.  The following plot shows the fitted model we called `model3` (again note the 'parallel lines').

```{r ranklines, eval = TRUE} 
model3 <- lm(score ~ bty_avg + rank, data = evals)
model3_aug <- augment(model3)

ggplot(data = model3_aug, mapping = aes(y = score, x = bty_avg, color = rank)) +
  geom_point(alpha = 0.3) +
  geom_line(aes(y = .fitted), lwd = 1)

``` 

<br>
